Paper Analysis

### 2024-10-15 Paper_WriteUp/Paper_Plots.qmd
working on making these plots even nicer

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(here)

@@

>>>>

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)

@@

```{r new boxplots}

player_pars |> 
  filter(param == 2) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  # geom_boxplot() +
  geom_density_ridges(alpha = 0.5, 
                      quantiles = 0.5, 
                      quantile_lines = T, 
                      rel_min_height = 0.005) + 
  # geom_density_ridges2(scale = 1, rel_min_height = 0.05) +
  # coord_flip() +
  labs(y = "", x = "Estimated W/L-Effect") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  xlim(c(-0.375, 0.375))

player_pars |> 
  filter(param == 1) |> 
  ggplot(aes(y = reorder(player_name, value, FUN = median), x = value)) +
  geom_boxplot(outliers = FALSE) +
  # coord_flip() +
  labs(y = "", x = "Estimated Player Effect") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed")
